Learning action models with minimal observability

### 2019-05-02 doc/aij18/minor-revision/experiments.tex
AIJ18-minor: rephrasing some points

\item {\bf Reproducibility}. We make fully available the compilation source code, the evaluation scripts and the used benchmarks at this repository {\em https://github.com/sjimenezgithub/strips-learning} so any experimental data reported in the paper is fully reproducible.
\end{itemize}

>>>>

\item {\bf Reproducibility}. We make fully available the compilation source code, the evaluation scripts and the used benchmarks at this repository {\em https://github.com/daineto/meta-planning} so any experimental data reported in the paper is fully reproducible.
\end{itemize}

### 2019-05-02 doc/aij18/minor-revision/learning_action_models.tex
AIJ18-minor: rephrasing some points

When the input plan trace contains observed actions, the extra conditional effects
$\{at_{i},plan(name(a_i),\Omega^{ar(a_i)},i)\}\rhd\{\neg at_{i},at_{i+1}\}_{\forall i\in [1,n]}$ are included in the $\mathsf{apply_{\xi,\omega}}$ actions to ensure that actions are applied in the same order as they appear in $\tau$. \textcolor{red}{As a side note, when the input trace contains all actions (\FO sequence of actions), this conditional effect is redefined as regular preconditions and effects. Doing so will make it impossible for the planner to execute apply actions outside of the observed ones. Additionally, for traces with \POstar or \FO state trajectories, we can force that only one apply action is executed between two observed states by adding the preconditions $\neg action_{applied}$.}\\

@@

There will be a validate action in $\pi_\Lambda$ for every observed state in $\tau$. The position of the validate actions in $\pi_\Lambda$ will be determined by the planner by checking that the state resulting after the execution of an apply action comprises the observed state $s_j\in\tau$. \textcolor{red}{If the input plan trace contains observed actions, we add an extra precondition, $at_{i+1}$, where $i$ is the index of the last observed action before the state we are validating. This additional precondition ensures that applied actions are also ordered with respect to the observed states}

>>>>

When the input plan trace contains \PO observed actions, the extra conditional effects
$\{at_{i},plan(name(a_i),\Omega^{ar(a_i)},i)\}\rhd\{\neg at_{i},at_{i+1}\}_{\forall i\in [1,n]}$ are included in the $\mathsf{apply_{\xi,\omega}}$ actions to ensure that actions are applied in the same order as they appear in $\tau$. \textcolor{red}{If the sequence of actions is FO, then this conditional effect is redefined as regular preconditions and effects in the apply actions. Doing so will make it impossible for the planner to execute apply actions other than the observed actions in the plan trace. Furthermore, for traces with \POstar or \FO state trajectories, we force that only one apply action is executed between two observed states by adding the precondition $\neg action_{applied}$ in every apply action.}

@@

There will be a validate action in $\pi_\Lambda$ for every observed state in $\tau$. The position of the validate actions in $\pi_\Lambda$ will be determined by the planner by checking that the state resulting after the execution of an apply action comprises the observed state $s_j\in\tau$. \textcolor{red}{If the input plan trace contains observed actions, we add an extra precondition, $at_{i+1}$, where $i$ is the index of the last observed action before the state we are validating. This additional precondition ensures that applied actions are also ordered with respect to the observed states.}
